---
title: "Homework10 Scrape data"
author: "Minzhi Liao"
date: "December 6, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set up

In this section we need `dplyr` and `tibble` to convert data to a `data.frame`, and `rvest` to deal with html stuffs.

```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(rvest))
```

## Scraping data

I pick yelp for the test. When you visit the website [yelp](https://www.yelp.com/search?find_desc=ramen&find_loc=South+Granville,+Vancouver,+BC) it actually shows the searching result for ramen near UBC. Now I want to get the name, address and rating of every restaurants.

The `html_nodes` paths are from [SelectorGadget](https://selectorgadget.com/). It is easy to use and works well in most cases.

```{r}
names <- read_html("https://www.yelp.com/search?find_desc=ramen&find_loc=UBC,+Vancouver,+BC") %>%
    html_nodes(".heading--h3__373c0__1n4Of.alternate__373c0__1uacp") %>%
    html_text()

ratings <- read_html("https://www.yelp.com/search?find_desc=ramen&find_loc=UBC,+Vancouver,+BC") %>%
    html_nodes(".i-stars__373c0__Y2F3O") %>%
    html_attr("aria-label")

address <- read_html("https://www.yelp.com/search?find_desc=ramen&find_loc=UBC,+Vancouver,+BC") %>%
    html_nodes(".u-space-t1 .domtags--span__373c0__1VGzF") %>%
    html_text()

area <- read_html("https://www.yelp.com/search?find_desc=ramen&find_loc=UBC,+Vancouver,+BC") %>%
    html_nodes(".text-align--right__373c0__3fmmn .border-color--default__373c0__2oFDT .border-color--default__373c0__2oFDT") %>%
    html_text()
```

Now we can combine things all up together.

```{r}
yelp_ramen <- tibble(
    name = names,
    rating = c("", ratings),
    address = address,
    area = area
)
```

Take a look at the `data.frame`. It is good, unless there are ads we can't remove at this moment in the first row. And the ad, which is `church's chicken` here, has no rating, so I need to fix this by adding a `""` at the very top.

```{r}
knitr::kable(head(yelp_ramen, 10))
```

Finally, we store the data for further processing, maybe.

```{r}
write.csv(yelp_ramen, "yelp_ramen.tsv")
```

Also note that there are no phone numbers available right now, because it is very complicated and not seperable by `html_nodes`. So we would need API queries for them. See the next chapter!
